### 2022-04-08 manuscript.tex
smallerfiures [ci skip]
This build is based on
https://github.com/scherzerthesis/thesis/commit/8fec467e841dcc3635a7c267f4d9f98ccfd8224c.

This commit was created by the following CI build and job:
https://github.com/scherzerthesis/thesis/commit/8fec467e841dcc3635a7c267f4d9f98ccfd8224c/checks
https://github.com/scherzerthesis/thesis/actions/runs/2116296334

This manuscript
(\href{https://scherzerthesis.github.io/thesis/v/2f23247bfc2eab5c45c9690621aa3a1e3a7242e9/}{permalink})
was automatically generated
from \href{https://github.com/scherzerthesis/thesis/tree/2f23247bfc2eab5c45c9690621aa3a1e3a7242e9}{scherzerthesis/thesis@2f23247}
on April 8, 2022.

>>>>

This manuscript
(\href{https://scherzerthesis.github.io/thesis/v/8fec467e841dcc3635a7c267f4d9f98ccfd8224c/}{permalink})
was automatically generated
from \href{https://github.com/scherzerthesis/thesis/tree/8fec467e841dcc3635a7c267f4d9f98ccfd8224c}{scherzerthesis/thesis@8fec467}
on April 8, 2022.
